Computer Science House By-Laws

### 2016-09-09 bylaws.tex
Add fixed percentage requirements for the different types of signatures to obtain an account

\bsection{Creation of Accounts}
Root Type Persons have the authority to manage user accounts for House systems. Before members may receive an account they must:
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of signatures in the Introductory Packet or successfully complete Introductory Evaluations.
\end{enumerate}

>>>>

\bsection{Creation of Accounts}
Root Type Persons have the authority to manage user accounts for House systems. Before members may receive an account they must:
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
	\item Successfully complete Introductory Evaluations or obtain greater than or equal to 60\% (rounded up to the nearest whole person) of each of the following types of signatures in the Introductory Packet:
		\begin{itemize}
			\item All Resident Active members and Executive Board members
			\item All Introductory members residing on floor
			\item Fifteen (15) Non-Resident and/or Alumni members (not including Non-Resident Executive Board members)
		\end{itemize}
\end{enumerate}
